---
title: 'intro to github'
output: html_document
date: "2026-01-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
ggplot(data=mtcars, aes(x=mpg))+
  geom_histogram(colour="black", fill="white, bins=15")+
  labs(x="Miles per Gallon")
```

section 2.3 
```{r}
## install.packages("palmerpenguins")
library(palmerpenguins)
library(tidyverse)
theme_set(theme_minimal())
penguins
```
Exercise 1. Make another plot of bill_length_mm with a different geom that is used for a single quantitative variable.

```{r}
ggplot(data = penguins, aes(x = bill_length_mm)) +
  geom_histogram() 
```


Exercise 2. Create a plot of a quantitative and a categorical variable in the penguins data set.

(side by side boxplot)
```{r}
ggplot(data=penguins,aes(x = species,y=bill_length_mm))+
  geom_bar(position="dodge")
```


Exercise 3. Modify the frequency plot made with geom_freqpoly() to use colour in two different ways:

a. change the colour of the line to any colour that R knows. A list of some colours can be found at this link.
```{r}
ggplot(data=penguins, aes(x=bill_length_mm))+ geom_freqpoly(colour="skyblue")

ggplot(data=penguins, aes(x=bill_length_mm))+ geom_freqpoly(aes(colour=species))
```


b. add a colour aesthetic to make three different frequency lines, one for each species of penguin.
```{r}

```

4. 
Recall that aes() aesthetics specified within the ggplot() function directly are called global aesthetics because every other <GEOM> will use them (unless specifically overridden) while aes() specified within a particular <GEOM> are called local aesthetics because only that particular <GEOM> will use them.

Modify the scatterplot and smoother so that

a. the points are coloured by species, but there is only one smoother instead of three.

```{r}
ggplot(data=penguins, aes(x=bill_length_mm))
```


b. there are three different coloured smoothers (one for each species) but the points are all the same colour.

5.
Create two different graphs that differ only by 1 of the 7 grammar of graphics parameters. Then, show your two graphs (but not your code) to a partner and see if they can identify which graphics parameter has been modified.

```{r}
ggplot(data=penguins, aes(x=bill_length_mm, 
```

